The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-11-15 OA.tex
cleaning of project folder - build replication files
limited and balanced attrition - analysis for internal validity

\vspace{.1in}

@@

\begin{figure}[H]
     \caption{Some Pawnshops}
    \label{PawnshopPicture}
    \begin{center}
    \begin{subfigure}{0.42\textwidth}
    \caption{Appraiser/tellers inside a pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
    \end{subfigure}

@@

    \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
    \end{subfigure}
    \begin{subfigure}{0.42\textwidth}
    \caption{Lost pawns which are for sale}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
    \end{subfigure}
    \end{center}
    \scriptsize
        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
\end{figure}

@@

Finally, Panel E of this table conducts a lasso logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.  This is a best guess of the outcome on censored loans.  Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -378 (main results) to -530 (censored loans predicted), and the APR from -34\% to -62\%.  Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.

@@

We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.  We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a training set and a test set.
These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
This avoids inferential problems that could arise from correlated unobservables within clusters.
In the first step, we apply the generalized random forest approach of \cite{atheygrf} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
\[
\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
\]
The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step. In particular, we estimate 
\begin{equation}
Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
\label{eq:chernreg}
\end{equation}
where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights. Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
\[
\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
\]
If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
Our estimate for $\beta_2$ is 2.5 with a one-sided heteroskedasticity-robust (HC3) of 0.43.
Thus we easily reject the null hypothesis of homogeneous treatment effects.

@@

The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:  $[-119, 122]$, and $[-4.2, 24.6]$.
Since both TUT (24) and ToT (122) estimates from the LATE approach lies inside these bounds, we cannot falsify the exclusion restriction. Moreover, the p-values associated with testing violation of inequalities \ref{eq:testable0}, and \ref{eq:testable1} is equal to one in both cases\footnote{We include the implementation of the validity test for the exclusion restriction for choosers and non-choosers in our STATA package.}.

>>>>

\vspace{.1in}
\subsection{Internal Validity}

\begin{figure}[H]
     \caption{Box-plot across arms}
    \label{boxplot_attrition}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
    \caption{Number of pawns}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
    \caption{Number of borrowers}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        This figure presents box-plot for the number of pawns and borrowers per branch-day across different arms. The solid black line represent the median, while the gray line represent the mean. The dots on top of the box-plot represent an implicit CDF. 
\end{figure}

% \begin{figure}[H]
%      \caption{Number of pawns and borrowers before and after the experiment}
%     \label{line_pawns_before_after}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/after_before_bal.pdf}
%     \scriptsize
%         This figure shows the number of pawns and borrowers before, during, and after the experiment for the different branches.
% \end{figure}

% \begin{figure}[H]
%      \caption{No discontinuity in the number of pawns before and after experiment}
%     \label{rd_pawns}
%        \begin{center}
%     \begin{subfigure}{0.45\textwidth}
%     \caption{Number of pawns - before}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/rd_before_pawns.pdf}
%     \end{subfigure}
%         \begin{subfigure}{0.45\textwidth}
%     \caption{Number of pawns - after}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/rd_after_pawns.pdf}
%     \end{subfigure}
%      \begin{subfigure}{0.42\textwidth}
%     \caption{Number of borrowers - before}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/rd_before_borr.pdf}
%     \end{subfigure}
%         \begin{subfigure}{0.45\textwidth}
%     \caption{Number of borrowers - after}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/rd_after_borr.pdf}
%     \end{subfigure}
%     \end{center}
%     \scriptsize
%         This figure shows the number of pawns and borrowers before, during, and after the experiment for the different branches.
% \end{figure}

@@

\begin{figure}[H]
     \caption{Some Pawnshops}
    \label{PawnshopPicture}
    \begin{center}
    \begin{subfigure}{0.405\textwidth}
    \caption{Appraiser/tellers inside a pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio9_.png}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio11_.png}
    \end{subfigure}

@@

    \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
    \end{subfigure}
    \begin{subfigure}{0.415\textwidth}
    \caption{Lost pawns which are for sale}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
    \end{subfigure}
    \end{center}
    \scriptsize
        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
\end{figure}

@@

Finally, Panel E of this table conducts a lasso logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.  This is a best guess of the outcome on censored loans.  Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -204 (main results) to -264 (censored loans predicted), and the APR from -11\% to -17\%.  Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.

@@

We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.  We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a training set and a test set.
These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
This avoids inferential problems that could arise from correlated unobservables within clusters.
In the first step, we apply the generalized random forest approach of \cite{atheygrf} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
\[
\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
\]
The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step. In particular, we estimate 
\begin{equation}
Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
\label{eq:chernreg}
\end{equation}
where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights. Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
\[
\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
\]
If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
Our estimate for $\beta_2$ is 2.56 with a one-sided heteroskedasticity-robust (HC3) of 0.43.
Thus we easily reject the null hypothesis of homogeneous treatment effects.

@@

The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:  $[-119, 123]$, and $[-4.2, 24.8]$.
Since both TUT (24) and ToT (122) estimates from the LATE approach lies inside these bounds, we cannot falsify the exclusion restriction. Moreover, the p-values associated with testing violation of inequalities \ref{eq:testable0}, and \ref{eq:testable1} is equal to one in both cases\footnote{We include the implementation of the validity test for the exclusion restriction for choosers and non-choosers in our STATA package.}.
